Active Learning for Level Set Estimation

### 2013-03-21 figurefactory/files/voned_cl_41_imp_1.tex
Add implicit extension

\begin{axis}[%
tick label style={font=\tiny},
label style={font=\tiny},
label shift={-4pt},
xlabel shift={-6pt},
legend style={font=\tiny},
view={0}{90},
width=\figurewidth,
height=\figureheight,
scale only axis,
xmin=0, xmax=2,
xtick={0, 0.5, 1, 1.5, 2},
ymin=-2, ymax=4,
tickwidth=0cm,
]

@@

\addplot [
color=darkgray,
solid,
only marks,
mark=square*,
mark size=2.5pt,
forget plot
]
coordinates{
 %(0,-2)
 (0.01,-2)(0.02,-2)(0.03,-2)(0.04,-2)(0.05,-2)(0.06,-2)(0.07,-2)(0.08,-2)(0.09,-2)(0.1,-2)(0.11,-2)(0.12,-2)(0.13,-2)(0.14,-2)(0.15,-2)(0.16,-2)(0.17,-2)(0.18,-2)(0.19,-2)(0.2,-2)(0.21,-2)(0.22,-2)(0.23,-2)(0.24,-2)(0.25,-2)(0.26,-2)(0.27,-2)(0.67,-2)(0.68,-2)(0.69,-2)(0.7,-2)(0.71,-2)(0.72,-2)(0.73,-2)(0.74,-2)(0.75,-2)(0.76,-2)(0.77,-2)(0.78,-2)(0.79,-2)(0.8,-2)(0.81,-2)(0.82,-2)(0.83,-2)(0.84,-2)(0.85,-2)(0.86,-2)(0.87,-2)(0.88,-2)(0.89,-2)(0.9,-2)(0.91,-2)(0.92,-2)(1.1,-2)(1.11,-2)(1.12,-2)(1.13,-2)(1.14,-2)(1.15,-2)(1.16,-2)(1.17,-2)(1.18,-2)(1.19,-2)(1.2,-2)(1.21,-2)(1.22,-2)(1.23,-2)(1.24,-2)(1.25,-2)(1.26,-2)(1.27,-2)(1.28,-2)(1.29,-2)(1.3,-2)(1.31,-2)(1.32,-2)(1.33,-2)(1.34,-2)(1.35,-2)(1.36,-2)(1.37,-2)(1.38,-2)(1.39,-2)(1.4,-2)(1.41,-2)(1.63,-2)(1.64,-2)(1.65,-2)(1.66,-2)(1.67,-2)(1.68,-2)(1.69,-2)(1.7,-2)(1.71,-2)(1.72,-2)(1.73,-2)(1.74,-2)(1.75,-2)(1.76,-2)(1.77,-2)(1.78,-2)(1.79,-2)(1.8,-2)(1.81,-2)(1.82,-2)(1.83,-2)(1.84,-2)(1.85,-2)(1.86,-2)(1.87,-2)(1.88,-2)(1.89,-2)(1.9,-2)(1.91,-2)(1.92,-2)(1.93,-2)(1.94,-2)(1.95,-2)(1.96,-2)(1.97,-2)(1.98,-2)(1.99,-2)
 %(2,-2) 
};

\addplot [
color=red!40!yellow,
solid,
only marks,
mark=square*,
mark size=2.5pt,
forget plot
]
coordinates{
 (0.28,-2)(0.29,-2)(0.3,-2)(0.31,-2)(0.32,-2)(0.33,-2)(0.34,-2)(0.35,-2)(0.36,-2)(0.37,-2)(0.38,-2)(0.39,-2)(0.4,-2)(0.41,-2)(0.42,-2)(0.43,-2)(0.44,-2)(0.45,-2)(0.46,-2)(0.47,-2)(0.48,-2)(0.49,-2)(0.5,-2)(0.51,-2)(0.52,-2)(0.53,-2)(0.54,-2)(0.55,-2)(0.56,-2)(0.57,-2)(0.58,-2)(0.59,-2)(0.6,-2)(0.61,-2)(0.62,-2)(0.63,-2)(0.64,-2)(0.65,-2)(0.66,-2)(1.42,-2)(1.43,-2)(1.44,-2)(1.45,-2)(1.46,-2)(1.47,-2)(1.48,-2)(1.49,-2)(1.5,-2)(1.51,-2)(1.52,-2)(1.53,-2)(1.54,-2)(1.55,-2)(1.56,-2)(1.57,-2)(1.58,-2)(1.59,-2)(1.6,-2)(1.61,-2)(1.62,-2) 
};

\addplot [
color=locol,
solid,
only marks,
mark=square*,
mark size=2.5pt,
forget plot
]
coordinates{
 (0.93,-2)(0.94,-2)(0.95,-2)(0.96,-2)(0.97,-2)(0.98,-2)(0.99,-2)(1,-2)(1.01,-2)(1.02,-2)(1.03,-2)(1.04,-2)(1.05,-2)(1.06,-2)(1.07,-2)(1.08,-2)(1.09,-2) 
};

\addplot [
color=red,
densely dashed,
line width=2.0pt,
forget plot
]
coordinates{
 (0,1.2)(2,1.2)
};

\addplot [
color=black,
solid,
line width=1.5pt,
mark=-,
mark size=3pt,
forget plot
]
coordinates{
 (1.23,0.0268)(1.23,1.9195)
};

\addplot [
color=yellow,
solid,
line width=4pt,
forget plot
]
coordinates{
 (1.23,1.2)(1.23,1.9195)
};

\addplot [
color=black,
solid,
line width=1.5pt,
mark=-,
mark size=3pt,
forget plot
]
coordinates{
 (0.23,0.9288)(0.23,3.8259)
};

\addplot [
color=yellow,
solid,
line width=4pt,
forget plot
]
coordinates{
 (0.23,0.9288)(0.23,1.2)
};

>>>>

\begin{axis}[%
tick label style={font=\tiny},
label style={font=\tiny},
label shift={-4pt},
xlabel shift={-6pt},
legend style={font=\tiny},
view={0}{90},
width=\figurewidth,
height=\figureheight,
scale only axis,
xmin=0, xmax=2,
xtick={0, 0.5, 1, 1.5, 2},
ymin=-2, ymax=4,
tickwidth=0.1cm,
]

@@

\addplot [
color=black,
densely dashed,
line width=1.5pt,
forget plot
]
coordinates{
 (0,3.825915)(2,3.825915)
};

\addplot [
color=black,
densely dashed,
line width=1.5pt,
forget plot
]
coordinates{
 (0,2.4975)(2,2.4975)
};

### 2013-03-21 msthpres.tex
Add implicit extension

\documentclass[10pt,mathserif,serif]{beamer}
%\documentclass[10pt,mathserif,serif,draft, handout]{beamer}

@@

\section{Extensions}

>>>>

\documentclass[10pt,mathserif,serif]{beamer}
%\documentclass[10pt,mathserif,serif,draft,handout]{beamer}

@@

\section{Two extensions}

\begin{frame}
\begin{itemize}
\item<1-> What if we don't know $h$?
\item<2-> Implicitly define the threshold level: $h = \omega \max_{\*x\in D} f(\*x),\ 0 < \omega < 1$
\item<5-> \iacl:
\begin{itemize}
\item<5-> Need to accurately estimate the maximum (don't exclude points that could be maximizers)
\item<6-> Slower classification
\end{itemize}
\end{itemize}
\begin{center}
\color{white}
\only<1-2>{\includegraphics[draft,width=3.77in]{figures/voned_cl_41_imp_1}}
\color{black}
\only<3>{\includegraphics[width=3.77in]{figures/voned_cl_41_imp_1}}
\only<4->{\includegraphics[width=3.77in]{figures/voned_cl_41_imp_2}}
\end{center}
\end{frame}

\begin{frame}
\begin{center}
\includegraphics<1-14>[width=4in]{figures/limno_bgape_ls}
\only<15>{\hspace{-1.9em}}
\includegraphics<15>[width=3.78in]{figures/limno_bgape_class_354}
\\

\only<1>{\color{white}\small{$t = 0$\\}}
\only<2>{\small{$t = 0$\\}}
\only<3>{\small{$t = 20$\\}}
\only<4>{\small{$t = 40$\\}}
\only<5>{\small{$t = 60$\\}}
\only<6>{\small{$t = 80$\\}}
\only<7>{\small{$t = 100$\\}}
\only<8>{\small{$t = 120$\\}}
\only<9>{\small{$t = 140$\\}}
\only<10>{\small{$t = 160$\\}}
\only<11>{\small{$t = 180$\\}}
\only<12>{\small{$t = 200$\\}}
%\only<13>{\small{$t = 220$\\}}
%\only<14>{\small{$t = 240$\\}}
\only<13>{\small{$t = 340$\\}}
%\only<16>{\small{$t = 280$\\}}
%\only<17>{\small{$t = 300$\\}}
%\only<18>{\small{$t = 320$\\}}
%\only<19>{\small{$t = 340$\\}}
\only<14>{\small{$t = 486$\\}}

\hspace{-1.9em}
\color{white}
\includegraphics<1>[draft,width=3.78in]{figures/limno_bgape_class_20}
\color{black}
\includegraphics<2>[width=3.78in]{figures/limno_bgape_imp_class_0}
\includegraphics<3>[width=3.78in]{figures/limno_bgape_imp_class_20}
\includegraphics<4>[width=3.78in]{figures/limno_bgape_imp_class_40}
\includegraphics<5>[width=3.78in]{figures/limno_bgape_imp_class_60}
\includegraphics<6>[width=3.78in]{figures/limno_bgape_imp_class_80}
\includegraphics<7>[width=3.78in]{figures/limno_bgape_imp_class_100}
\includegraphics<8>[width=3.78in]{figures/limno_bgape_imp_class_120}
\includegraphics<9>[width=3.78in]{figures/limno_bgape_imp_class_140}
\includegraphics<10>[width=3.78in]{figures/limno_bgape_imp_class_160}
\includegraphics<11>[width=3.78in]{figures/limno_bgape_imp_class_180}
\includegraphics<12>[width=3.78in]{figures/limno_bgape_imp_class_200}
\includegraphics<13>[width=3.78in]{figures/limno_bgape_imp_class_340}
\includegraphics<14->[width=3.78in]{figures/limno_bgape_imp_class_486}
\end{center}
\end{frame}

\begin{frame}
\begin{center}
\includegraphics[width=2.3in]{figures/ev_chl_imp}
\includegraphics[width=2.3in]{figures/ev_bgape_imp}
\end{center}
\end{frame}
